\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\usepackage{hyperref} % Add hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\input{glyphtounicode}
\usepackage{xcolor}
\color{black} % Add this line to set the text color


%----------FONT OPTIONS----------
% serif
\usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Vivek Chennupati} \\ \vspace{1pt}
    \small 
    \href{tel:9642175872}{\raisebox{-0.1\height}\faPhone\ 9642175872} ~ \href{mailto:vivekchennupati126@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{vivekchennupati126@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/vivekchennupati/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/vivekchennupati}}  ~
    \vspace{-6pt}
\end{center}



% \section{Summary of Qualifications}
% \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{
%       \item{
%         Results-driven Full Stack Developer with expertise in Django, Python, and JavaScript.
%       }
%       \item{
%         Proven track record of developing dynamic e-commerce platforms, improving user experiences, and implementing effective CI/CD pipelines.
%       }
%     }
%  \end{itemize}
%  \vspace{-16pt}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B.Tech in Information Technology}{2020-2023}
      {MLR Institute of Technology, Hyderabad, Telangana}{CGPA: 7.2/10}
    \resumeSubheading
      {Diploma in Mechanical Engineering}{2017-2020}
      {St. Peter's Engineering College, Hyderabad, Telangana}{Percentage: 75.4 \%}
    \resumeSubheading
      {10th Grade (SSC)}{March 2017}
      {St. Alphonsa’s High School, Hyderabad, Telangana}{CGPA: 8.5/10}
  \resumeSubHeadingListEnd



\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
    {Tierra Agrotech Limited}{{July 2023 - Present}}
    {Web Developer}{Hyderabad}
    \resumeItemListStart
      \resumeItem{Developed a Django-based e-commerce platform with features like a payment system that sends automatic invoices via email, ensuring a seamless checkout process.}
      \resumeItem{Built an efficient admin panel for managing products, blogs, and other e-commerce operations.}
      \resumeItem{Implemented coupon codes, promotional email systems, and integrated Google Merchant for enhanced marketing and sales operations.}
      \resumeItem{Utilized Django backend with HTML, CSS, JS, and Bootstrap for the frontend, ensuring a modern and responsive user interface.}
      \resumeItem{Handled site content management, inventory tracking, and real-time order management, keeping the site running smoothly.}
      \resumeItem{Managed code versioning using GitHub and established CI/CD for deployment, ensuring continuous integration and smooth deployment cycles.}
      \resumeItem{Oversaw ongoing site maintenance, including performance optimization, bug fixes, and feature updates.}
      \resumeItem{
      Website :  \underline{\href{https://mekisan.in}{mekisan.in}}
      }
    \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Dynamic Website Generator from Resume Upload} $|$ \emph{ Django, HTML/CSS, JavaScript, AWS}}{Jan 2023}
          \resumeItemListStart
            \resumeItem{Developed a Django-based project enabling users to upload resumes for automated extraction of details.}
            \resumeItem{Implemented a resume parser to extract user details and dynamically generate a website with the parsed information.}
            \resumeItem{Utilized Django's functionalities to process resumes and dynamically create web content based on extracted details.}
            \resumeItem{Enhanced user experience by automating the process of creating personalized websites from uploaded resumes.}
          \resumeItemListEnd
           \vspace{-16pt}


\resumeProjectHeading
    {\textbf{IoT-Based Home Automation System} $|$ \emph{Arduino, IoT, Web Development}}{Aug 2022}
    \resumeItemListStart
        \resumeItem{Created a remote home automation setup using Arduino and IoT technologies.}
        \resumeItem{Utilized sensors and Arduino for device internet connectivity and communication.}
        \resumeItem{Implemented secure communication via Blink server for reliable data transfer.}
        \resumeItem{Developed a user-friendly web app for device control and notifications.}
        \resumeItem{Resulted in efficient device management, saving time and energy for users.}
    \resumeItemListEnd
\vspace{-16pt}

    
\resumeProjectHeading
    {\textbf{Manju Farmhouse Website} $|$ \emph{Django, HTML/CSS, JavaScript}}{May-2024}
    \resumeItemListStart
        \resumeItem{Developed a dynamic website for a farmhouse using Django, featuring detailed property information and booking options.}
        \resumeItem{Showcased amenities and events with a user-friendly interface and seamless navigation.}
        \resumeItem{Built a custom admin panel for easy updates to content, galleries, and bookings.}
        \resumeItem{Created a platform to effectively promote the farmhouse and attract potential visitors.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
        \textbf{Languages}{: Python, Java} \\
        \textbf{Web Frameworks}{: Django, ReactJs} \\
        \textbf{Databases}{: MySQL, SQLite} \\
        \textbf{Development Tools}{: Git \& Github, Nginx, AWS CICD pipeline} \\
        \textbf{Content Management Systems}{: Wordpress, Elementor} \\
        \textbf{Other Skills}{: Payment Gateway Integration, Django RestAPI, Django ORM} \\
      }
    }
 \end{itemize}
 \vspace{-16pt}


\section{Courses and Certificates}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Full Stack Development}{Coursera}
            {Duration: (3 Months)}{}
        \resumeSubheading
            {Introduction to Git and GitHub}{Google}
            {Duration: (1 Month)}{}
        \resumeSubheading
            {Introduction to Python}{Coding Ninjas}
            {Duration: (2 Months)}{}
    \resumeSubHeadingListEnd
\end{document}
